\section{Appendix 1}

\begin{itemize}[noitemsep]
    \item What is the problem domain or context of the visualization under consideration?
    \item Which tasks can be achieved with this visualization?
    \item Tufte’s principles of graphical integrity:
        \begin{itemize}[noitemsep]
            \item Are the scales appropriately labeled?
            \item Is the Lie factor high?
            \item Does the visualization show data variation and not design variation?
        \end{itemize}
    \item Tufte’s visualization design principles, are they adhered to?
        \begin{itemize}[noitemsep]
            \item Maximize the data-ink ratio.
            \item Avoid chart junk.
            \item Increase data density.
            \item Layer information.
        \end{itemize}
    \item Graphic design principles:
        \begin{itemize}[noitemsep]
            \item How is contrast used? What kind of contrast is used?
            \item How is repetition used?
            \item How is alignment used?
            \item How is proximity used?
        \end{itemize}
    \item Comment on the visual encodings that are used.
        \begin{itemize}[noitemsep]
            \item Which visual encodings are used?
            \item Are the visual encodings appropriate?
        \end{itemize}
    \item Comment on subjective dimensions such as aesthetics, style, playfulness
    and vividness.
    \item What is the intended goal of the visualization and is that goal achieved?
    \item Are there any things you would do differently, and why?
\end{itemize}
